Mechanization of Separation in Generic Extensions

### 2019-01-06 LICS/renaming.tex
comentario del final a medias

% All our uses of this lemma involve concrete renamings on small
% numbers, but we also tested it with more abstract renamings for
% arbitrary numbers. We think that it should be possible, and clearer,
% to express all the current renamings in the theory \isa{Formula} using
% our approach.

>>>>

All our uses of this lemma involve concrete renamings on small
numbers, but we also tested it with more abstract one for
arbitrary numbers. All the renamings of the first kind follow the
same pattern and, more importantly, share equal proofs. We would like
to develop some \texttt{ML} tools in order to automatize this.
%% We think that it should be possible, and clearer,
%% to express all the current renamings in the theory \isa{Formula} using
%% our approach.
